Estimation of the perceived time of presence of sources in urban acoustic environment using deep learning techniques

### 2019-06-04 paper/paperV1.tex
abstract 1

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
Need for characterization of soundscape perception through objective descriptors, 
Dependance on sources, level measurements insufficient
sensor networks + deep learning

For such purposes, a corpus of simulated sound scenes is proposed that allows the use of ground truth source contributions for the development of learning-based models. It includes semi-randomly generated original scenarios representative of the urban environment. This simulated corpus is shown through a listening experiment to yield similar perceptual responses compared to recorded sound scenes.

to predict the perceived source presence in 1~s time frames with labels obtained from

This model is compared to both perceptual and physical baseline models obtained from the perceptual experiment's data in the context of pleasantness prediction
\end{abstract}
